Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-16 p2/axioms.tex
New proof for the correctness of reconciliation
Removed unused results
Output labels for easier reviewing

\section{Investigating Command Pairs}\label{section_axioms}

@@

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
Sequences are also partial endofunctions on filesystems, defined only if all commands it contains succeed in the given order.
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mylem}\label{equiv_on_fs}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
% TODO APPENDIX
If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we know $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
\end{proof}

@@

\begin{myax}\label{ax_separate_commute}
Commands on incomparable nodes commute:
$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
\end{myax}

\begin{myax}\label{ax_separate_nobreaks}
Commands on incomparable nodes do not break all filesystems:
$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
\end{myax}

\begin{myax}\label{ax_same_breaks}
Commands on the same node break every filesystem if their types are incompatible:
$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
\end{myax}

\begin{myax}\label{ax_same_emptyseq}
Commands on the same node simplify:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
or $\cxw=\cdd$.
\end{myax}

\begin{myax}\label{ax_same_singlec}
Commands on the same node simplify:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
\end{myax}

\begin{myax}\label{ax_distantrel_breaks}
Commands on distant relatives break all filesystems:
$\cxynnv\cc\czwnv \equiv \cbrk$
and $\czwnv\cc\cxynnv \equiv\cbrk$
where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
(More intuitively, if $\czw\neq\cbb$ then either before or after $\czwnv$, the filesystem at
$n$ is not empty, and therefore there must be a directory at all ancestors of $n$, including at a child of $\nn$.
Consequently $\cxynnv$ will break the filesystem as either before or after it the filesystem at $\nn$
does not have a directory.)
\end{myax}

@@

\begin{myax}\label{ax_directchild_breaks}
All other commands on a child break every filesystem:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
and the pair is not a construction pair.
As we shall see, this can be extended to \cref{simple_distant_pairs}.
% TODO
\end{myax}

@@

\begin{myax}\label{ax_directparent_breaks}
All other commands on a parent break every filesystem:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
and the pair is not a destruction pair.
This can also be extended to \cref{simple_distant_pairs}.
% TODO
\end{myax}

@@

\begin{myax}\label{ax_child_assert}
An assertion command can be added on a descendant node:
\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
where $\nn\descendant n$ and $\cxy\neq\cdd$.
(Note that this and next rule is true because the assertion command is
adjacent to the original command.)
\end{myax}

\begin{myax}\label{ax_parent_assert}
An assertion command can be added on an ancestor node:
\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
where $\nn\descendant n$ and $\cxy\neq\cbb$.
\end{myax}

\begin{myax}\label{ax_assert}
Assertion commands can be removed:
$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
% $\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
\end{myax}

@@

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\label{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they commute and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \wrksx{\czwnv\cc\cxynv}. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
We also write $\alpha\indep B$ iff $\{\alpha\}\indep B$.
\end{mydef}

@@

\begin{mylem}\label{incomparable_is_independent}
Two different commands that are not assertion commands are independent iff the nodes they change are incomparable. In other words,
\[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
if $\cxy\neq\czw$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
\end{mylem}
\begin{proof}
This is easy to show based on the output of the program that investigates the behavior of command pairs.
However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
in the following way.

>>>>

\section{Investigating Command Pairs}\mlabel{section_axioms}

@@

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
Sequences are also partial endofunctions on filesystems, defined only if all commands it contains succeed in the given order.
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mylem}\mlabel{equiv_on_fs}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
% TODO APPENDIX
If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we know $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
\end{proof}

@@

\begin{myax}\mlabel{ax_separate_commute}
Commands on incomparable nodes commute:
$\cxynv\cc\czwmv \equiv \czwmv\cc\cxynv$ where $n\unrel m$.
\end{myax}

\begin{myax}\mlabel{ax_separate_nobreaks}
Commands on incomparable nodes do not break all filesystems:
$\wrksx{\cxynv\cc\czwmv}$ where $n\unrel m$.
\end{myax}

\begin{myax}\mlabel{ax_same_breaks}
Commands on the same node break every filesystem if their types are incompatible:
$\cxynv\cc\czwnv \equiv \cbrk$ where $[y]\ne [z]$.
\end{myax}

\begin{myax}\mlabel{ax_same_emptyseq}
Commands on the same node simplify:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
or $\cxw=\cdd$.
\end{myax}

\begin{myax}\mlabel{ax_same_singlec}
Commands on the same node simplify:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.
\end{myax}

\begin{myax}\mlabel{ax_distantrel_breaks}
Commands on distant relatives break all filesystems:
$\cxynnv\cc\czwnv \equiv \cbrk$
and $\czwnv\cc\cxynnv \equiv\cbrk$
where $\nn\descendant n$ and $\nn\neq\parent(n)$, and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
(More intuitively, if $\czw\neq\cbb$ then either before or after $\czwnv$, the filesystem at
$n$ is not empty, and therefore there must be a directory at all ancestors of $n$, including at a child of $\nn$.
Consequently $\cxynnv$ will break the filesystem as either before or after it the filesystem at $\nn$
does not have a directory.)
\end{myax}

@@

\begin{myax}\mlabel{ax_directchild_breaks}
All other commands on a child break every filesystem:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
and the pair is not a construction pair.
As we shall see, this can be extended to \cref{simple_distant_pairs}.
% TODO Delete this rule
\end{myax}

@@

\begin{myax}\mlabel{ax_directparent_breaks}
All other commands on a parent break every filesystem:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
and the pair is not a destruction pair.
This can also be extended to \cref{simple_distant_pairs}.
% TODO Delete this rule
\end{myax}

@@

\begin{myax}\mlabel{ax_child_assert}
An assertion command can be added on a descendant node:
\[ \cbba{n}\cc\cxynnv \equiv \cxynnv \equiv \cxynnv\cc\cbba{n} \] 
where $\nn\descendant n$ and $\cxy\neq\cdd$.
(Note that this and next rule is true because the assertion command is
adjacent to the original command.)
\end{myax}

\begin{myax}\mlabel{ax_parent_assert}
An assertion command can be added on an ancestor node:
\[ \cdda{\nn}\cc\cxynv \equiv \cxynv \equiv \cxynv\cc\cdda{\nn} \]
where $\nn\descendant n$ and $\cxy\neq\cbb$.
\end{myax}

\begin{myax}\mlabel{ax_assert}
Assertion commands can be removed:
$\cdda{n}\eqext\emptyseq$ and $\cbba{n}\eqext\emptyseq$.
% $\cxynv \eqext \emptyseq$ where $\cxy=\cbb$ or $\cxy=\cdd$.
\end{myax}

@@

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets of commands]\mlabel{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they commute and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \wrksx{\czwnv\cc\cxynv}. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
We also write $\alpha\indep B$ iff $\{\alpha\}\indep B$.
\end{mydef}

@@

\begin{mylem}\mlabel{incomparable_is_independent}
Two different commands that are not assertion commands are independent iff the nodes they change are incomparable. In other words,
\[ \cxynv\indep\czwmv \Longleftrightarrow n\unrel m \]
if $\cxy\neq\czw$ and none of $\cxy$ and $\cxw$ is $\cbb$ or $\cdd$.
\end{mylem}
\begin{proof}
This is easy to show based on the output of the program that investigates the behavior of command pairs.
However, this proposition can also be derived from the \namecrefs{ax_separate_commute} already listed
in the following way.

### 2017-10-16 p2/ordering.tex
Fixed the soundness proof. Inverses are needed after all.
Removed unused results
Output labels for easier reviewing

\subsection{Ordering commands}\label{ordering}

@@

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of sequences
that are all permutations of the commands in $S$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

\begin{myclm}\label{subseq_in_orderset}
For simple sequences $S$ and $T$,
if $T\in\orderset{S}$, then for any subsequence of $S$, $S_0$,
and for the corresponding subsequence of $T$, $T_0$, which
contains the same commands but in the order they are found in $T$,
$T_0\in\orderset{S_0}$ must hold.
\end{myclm}
\begin{proof}
This is because
if there are no command pairs in $T$ not conforming to \cref{def_orderset},
then there cannot be any in $T_0$.
\end{proof}

\begin{mylem}\label{simple_distant_pairs}
For any simple sequence $\wrksx{S}$,
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
\end{mylem}
\begin{proof}
Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

@@

\begin{mycor}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that placed next to each other do not form
a construction or destruction pair.
Let them be $\cxynv$ and $\czwmv$.
By \cref{ax_directchild_breaks,ax_directparent_breaks}
we know
$\cxynv\cc\czwmv\equiv\cbrk$, which is a subsequence of $S'$,
and therefore by \cref{simple_distant_pairs}, $S'\equiv\cbrk$.
\end{proof}

\begin{mylem}\label{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
Without loss of generality, we can assume that $\nn\neq\parent(n)$.
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

@@

\begin{mylem}\label{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv \wrksx{B}$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
% BACK_TO_THE_FS
% TODO Rule?
We use a proof by contradiction. Let $A$ and $B$ be simple sequences
such that $A\equiv \wrksx{B}$,
and $\FS$ be a filesystem that they are defined on.

@@

\begin{mylem}\label{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = [S]_\equiv \cap \setssmp. \]
\end{mylem}

@@

%% TODO Define set operations on sequences?
% \noindent As a specific case, we can regard a simple sequence $S$
% as a set, and use the above algorithm to generate all possible orderings
% of the commands it contains.

TODO TODO TODO -- ONLY USED ONCE WHERE INTERNALS OF OLD PROOF ARE USED
\begin{mycor}\label{lemma:neighbor}
If a simple sequence $S$ contains commands on both $n$ and $\parent(n)$, then
there is a simple $S'\equiv S$ in which they are next to each other.
\end{mycor}

>>>>

% TODO Commuting commands important as we need to establish order

\subsection{Ordering commands}\mlabel{ordering}

@@

\begin{mydef}[$\ordersetsign$]\mlabel{def_orderset}
For a simple set or sequence of commands $S$,
we use $\orderset{S}$ to denote the set of sequences
that are all permutations of the commands in $S$
for which the following holds:
for all subsequences $\cxynv\cc\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

@@

\begin{myclm}\mlabel{subseq_in_orderset}
For simple sequences $S$ and $T$,
if $T\in\orderset{S}$, then for any subsequence of $S$, $S_0$,
and for the corresponding subsequence of $T$, $T_0$, which
contains the same commands but in the order they are found in $T$,
$T_0\in\orderset{S_0}$ must hold.
\end{myclm}
\begin{proof}
This is because
if there are no command pairs in $T$ not conforming to \cref{def_orderset},
then there cannot be any in $T_0$.
\end{proof}

\begin{mylem}\mlabel{simple_distant_pairs}
For any simple sequence $\wrksx{S}$,
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
\end{mylem}
\begin{proof}
Informally speaking, the proposition means that
the two commands must form a construction or destruction pair even
if they are not next to each other.
This is true because in simple sequences
there cannot be another command on $n$ or $m$,
so if the commands are incompatible, no command between them can change that.
In fact, this \namecref{simple_distant_pairs} is the general case
of \cref{ax_directchild_breaks,ax_directparent_breaks}.

@@

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that placed next to each other do not form
a construction or destruction pair.
Let them be $\cxynv$ and $\czwmv$.
By \cref{ax_directchild_breaks,ax_directparent_breaks}
we know
$\cxynv\cc\czwmv\equiv\cbrk$, which is a subsequence of $S'$,
and therefore by \cref{simple_distant_pairs}, $S'\equiv\cbrk$.
\end{proof}

\begin{mylem}\mlabel{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
Without loss of generality, we can assume that $\nn\neq\parent(n)$.
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

@@

\begin{mylem}\mlabel{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv \wrksx{B}$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
% BACK_TO_THE_FS
% TODO Rule?
We use a proof by contradiction. Let $A$ and $B$ be simple sequences
such that $A\equiv \wrksx{B}$,
and $\FS$ be a filesystem that they are defined on.

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = [S]_\equiv \cap \setssmp. \]
\end{mylem}

@@

### 2017-10-16 p2/rec-complete.tex
New "works" symbol, fixes
Output labels for easier reviewing

\begin{myth}\label{rec_is_complete}
If $A$ and $B$ are simple sequences,
and we select a sequence $S\subset \amb$ so that
it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
(that is, $S$ breaks all possible $\FS_B$ replicas),
or it changes a node that $B$ has already changed to a different value,
that is, it overrides a change in $\FS_B$.
\end{myth}
Such an override could occur if a given node was modified differently in
$A$ and $B$ (to different values but the same type), which is clearly
a conflict that should be marked for review
by a human or a different system.
\begin{proof}
The proof is similar to the ones we have seen above.
Without loss of generality, we assume that $\cxynv$ is the first command in $S$
that is not independent of $\bmanp$.
If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
Let us also split $\bmanp$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
From \cref{can_move_intersection} we know that
$B\cc S \equiv \acb\cc\bma\cc S$.
We also know that commands in $S_0$ and $\bmanp$ commute, and so this is equivalent to
$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
Expanding $\bmanp$ and swapping $T_1$ and $\cxynv$ we get
\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]

@@

Clearly $[q]=[z]$ (from \cref{worksinputmatch}), and from the construction and destruction
pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
$\cqrmv = \czwmv$.
This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.

>>>>

\begin{myth}\mlabel{rec_is_complete}
If $A$ and $B$ are simple sequences,
and we select a sequence $S\subset \amb$ so that
it contains a command $\cxynv$ for which $\cxynv\nindep\bma$,
then $B\cc S$ either breaks all filesystems $A$ and $B$ do not break
(that is, $S$ breaks all possible $\FS_B$ replicas),
or it changes a node that $B$ has already changed to a different value,
that is, it overrides a change in $\FS_B$.
\end{myth}
Such an override could occur if a given node was modified differently in
$A$ and $B$ (to different values but the same type), which is clearly
a conflict that should be marked for review
by a human or a different system.
\begin{proof}
The proof is similar to the ones we have seen above.
Without loss of generality, we assume that $\cxynv$ is the first command in $S$
that is not independent of $\bmanp$.
If so, we can split $S$ into $S_0\cc\cxynv\cc S_1$ where $S_0\indep\bma$.
Let us also split $\bmanp$ into $T_0\cc\czwmv\cc T_1$ where $T_1\indep\cxynv$.
From \cref{can_move_intersection} we know that
$B\cc S \equiv \acb\cc\bma\cc S$.
We also know that commands in $S_0$ and $\bmanp$ commute, and so this is equivalent to
$\acb\cc S_0\cc\bma\cc\cxynv\cc S_1$.
Expanding $\bmanp$ and swapping $T_1$ and $\cxynv$ we get
\[ \acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv\cc T_1\cc S_1. \]

@@

Clearly $[q]=[z]$ (from \cref{worksinputmatch}), and from the construction and destruction
pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
As $|\setd|=1$ and $|\setb|=1$, this also means that $::v_R=v_W::$ and therefore
$\cqrmv = \czwmv$.
This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.

### 2017-10-16 p2/rec-intro.tex
Output labels for easier reviewing

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{mydef}

>>>>

\begin{mydef}[Reconciliation]\mlabel{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{mydef}

### 2017-10-16 p2/rec-sound.tex
Output labels for easier reviewing

\begin{myth}\label{reconciliation_correct}
If $A$ and $B$ are simple, then $\worksmbx{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{myth}

@@

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences for which $\worksmnilb{A, B}$.
Then $A$ can be separated into their intersection and the remaining commands:
\[ \acb\cc\amb \in \orderset{A}. \]
\end{mylem}

@@

Our theorem is therefore proven if we prove the following lemma.
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\begin{mylem}\label{reconciliation_correct_part}
If
{\condSimple} $S$ and $T$ are simple sequences,
{\condDisj} $S\cap T=\emptyset$,
and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
then
$\worksmbx{S,T}{S^*}$.
\end{mylem}

>>>>

\begin{myth}\mlabel{reconciliation_correct}
If $A$ and $B$ are simple, then $\worksmbx{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \ords{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp }. \]
\end{myth}

@@

\begin{mylem}\mlabel{can_move_intersection}
Let $A$ and $B$ be two simple sequences for which $\worksmnilb{A, B}$.
Then $A$ can be separated into their intersection and the remaining commands:
\[ \acb\cc\amb \in \orderset{A}. \]
\end{mylem}

@@

Our theorem is therefore proven if we prove the following lemma.
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\begin{mylem}\mlabel{reconciliation_correct_part}
If
{\condSimple} $S$ and $T$ are simple sequences,
{\condDisj} $S\cap T=\emptyset$,
and {\condApr} $S^*$ is the largest subset of $S$ where $S^*\indep T$,
then
$\worksmbx{S,T}{S^*}$.
\end{mylem}

### 2017-10-16 p2/upd-correct.tex
Output labels for easier reviewing

\begin{myth}\label{update_works}
A sequence of commands returned by the update detector
when comparing the non-broken $\FS^*$ to the original $\FS$
will not break $\FS$ if it is applied to it.
\end{myth}
\begin{proof}
Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
be the filesystem after the changes we intend to detect.
Let us assume that some mechanism recorded all changes that occurred
to $\FS$ until it reached the state $\FS^*$.
Our set if commands is sufficient to record any change, as
there are commands for every input and output type pair, therefore
we know that the changes can be recorded as a sequence of commands $S$
where $S\aFS=\FS^*$.
Note that $S$ will not contain assertion commands, as they do not
represent an actual change in the filesystem.

>>>>

\begin{myth}\mlabel{update_works}
A sequence of commands returned by the update detector
when comparing the non-broken $\FS^*$ to the original $\FS$
will not break $\FS$ if it is applied to it.
\end{myth}
\begin{proof}
Let $\FS\neq\fsbroken$ be the original filesystem, and $\FS^*\neq\fsbroken$
be the filesystem after the changes we intend to detect.
Let us assume that some mechanism recorded all changes that occurred
to $\FS$ until it reached the state $\FS^*$.
Our set if commands is sufficient to record any change, as
there are commands for every input and output type pair, therefore
we know that the changes can be recorded as a sequence of commands $S$
where $S\aFS=\FS^*$.
Note that $S$ will not contain assertion commands, as they do not
represent an actual change in the filesystem.
